From Reversible Programs to \\ Univalent Universes and Back

### 2021-06-30 Pi+/paper/reversible1.tex
diagrams for permutations in sec 3.2

Using the definition, we have:
\[\begin{array}{rcl}
    \mathit{enum}(\onet + (\onet + \onet)) &=& [ \inlv{\Acon{tt}},\inrv{(\inlv{\Acon{tt}})}, \inrv{(\inrv{\Acon{tt}})} ] \\
    \mathit{enum}((\onet + \onet) + \onet) &=& [ \inlv{(\inlv{\Acon{tt}})},  \inlv{(\inrv{\Acon{tt}})}, \inrv{\Acon{tt}} ]
  \end{array}\]
Thus, $\assoclp~(\inlv{\Acon{tt}})$ applies the permutation $(0~1~2)$ to the index of $\inlv{\Acon{tt}}$ which is 0 and
produces index 0 in the $(\onet + \onet) + \onet$ type corresponding to value $\inlv{(\inlv{\Acon{tt}})}$. Similarly,
$\swapp~(\inlv{\Acon{tt}})$ applies the permutation $(2~0~1)$ to the index of $\inlv{\Acon{tt}}$ which is 0 and produces
index 2 in the $(\onet + \onet) + \onet)$ type corresponding to value $\inrv{\Acon{tt}}$.

>>>>

Using the definition, we have:
\[\begin{array}{rcl}
    \mathit{enum}(\onet + (\onet + \onet)) &=& [ \inlv{\Acon{tt}},~\inrv{(\inlv{\Acon{tt}})},~\inrv{(\inrv{\Acon{tt}})} ] \\
    \mathit{enum}((\onet + \onet) + \onet) &=& [ \inlv{(\inlv{\Acon{tt}})},~\inlv{(\inrv{\Acon{tt}})},~\inrv{\Acon{tt}} ]
\end{array}\]
Thus, as shown in the diagrams below, $\assoclp~(\inlv{\Acon{tt}})$ applies the permutation $(0~1~2)$ to the index of
$\inlv{\Acon{tt}}$ which is 0 and produces index 0 in the $(\onet + \onet) + \onet$ type corresponding to value
$\inlv{(\inlv{\Acon{tt}})}$. Similarly, $\swapp~(\inlv{\Acon{tt}})$ applies the permutation $(2~0~1)$ to the index of
$\inlv{\Acon{tt}}$ which is 0 and produces index 2 in the $(\onet + \onet) + \onet)$ type corresponding to value
$\inrv{\Acon{tt}}$.

\begin{center}
  \input{assoc-perm.tikz}
  \qquad
  \input{swap-perm.tikz}
\end{center}
